### 2021-02-26 yfcc100m/paper/vldb2021/eval.tex
Minor update on eval
Minor fixes

It is worth noting that the images are stored in a shared repository
(ext4 filesystem on a RAID 6 configuration of 16TB) that both
Apache WebServer and VDMS have direct access.
In the case of videos, only the first frame is used for the image search.
% More information and evaluation on video-specific functionalities can be found
% in the appendix of this work.
In the case of the baselines, metadata is
stored in MySQL and PostgreSQL using an attached SSD disk.
Even if VDMS has native support for Optane Persistent Memory,
we do not use it in this experiment because of fairness of
comparison with respect to MySQL and PostgreSQL, which were not designed for
Persistent Memory type of storage.
The benefits of Persistent Memory for metadata and a full evaluation of
the PMGD subsystem is material for another paper,
and outside the scope of this evaluation.
For this experiment, in the case of VDMS we simply use a similar
attached SSD disk to store metadata.
Even if PMGD, the graph database used by VDMS, is designed for persistent memory,
it can deliver good performance when using SSDs directly.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\textwidth]{figures/plot_th_56_query_times_speedup_postgresql}
\caption{Summary of performance gains for all queries.
We see up to 364x speedup (\textit{q1}), and an average of about 85x.
More importantly, we see that the speedup grow as the database size increases,
showing that VDMS scales better than the PostGreSQL baseline.}
\label{fig:summary_postgresql}
\end{figure*}

>>>>

It is worth noting that the images are stored in a shared repository
(ext4 filesystem on a RAID 5 configuration of 16TB) that both
Apache WebServer and VDMS have direct access.
In the case of videos, only the first frame is used for the image search.
% More information and evaluation on video-specific functionalities can be found
% in the appendix of this work.
In the case of the baselines, metadata is
stored in MySQL and PostgreSQL using an attached SSD disk.
Even if VDMS has native support for Optane Persistent Memory,
we do not use it in this experiment because of fairness of
comparison with respect to MySQL and PostgreSQL, which were not designed for
Persistent Memory type of storage.
The benefits of Persistent Memory for metadata and a full evaluation of
the PMGD subsystem is material for another paper,
and outside the scope of this evaluation.
For this experiment, in the case of VDMS we simply use a similar
attached SSD disk to store metadata.
Even if PMGD, the graph database used by VDMS, is designed for persistent memory,
it can deliver good performance when using SSDs directly.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\textwidth]{figures/plot_th_56_query_times_speedup_postgresql}
\caption{Summary of performance gains for all queries.
We see up to 364x speedup (\textit{q1}), and an average of about 85x.
More importantly, we see that the speedup grow as the database size increases,
showing that VDMS scales better than the PostgreSQL+Apache baseline.}
\label{fig:summary_postgresql}
\end{figure*}
